---
title: "TODO
"
author:  Pascal Belleau and Astrid Deschênes
output:
  html_document:
    toc: true
bibliography: biblio.bibtex
vignette: >
  %\VignetteIndexEntry{TODO}
  %\VignettePackage{subnetsim}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r style, echo = FALSE, results = 'asis', warning=FALSE, message=FALSE}
library(knitr)
library(subnetsim)
```

<br />

**Package**: `r packageDescription("subnetsim")[["Package"]]` <br />
**Authors**: `r packageDescription("subnetsim")[["Author"]]` <br />
**Version**: `r packageDescription("subnetsim")$Version` <br />
**Compiled date**: `r Sys.Date()` <br />
**License**: `r packageDescription("subnetsim")[["License"]]` <br />


# Licensing 

The `r packageDescription("subnetsim")[["Package"]]` package and the underlying 
`r packageDescription("subnetsim")[["Package"]]` code 
are distributed under the Artistic license 2.0. You are free to use and 
redistribute this software.


# Introduction

TODO: Presentation du network, lien, noeuds

Network science is a cross-disciplinary domain that focuses on the representation, analysis and modeling of complex biological, social and technological systems as networks or graphs.

A network model is a mathematical model that is designed to represent entities and their relationships in a system. A network is a collection of nodes (or vertices or sites or actors) joined by edges (or links or bonds or ties). Throught the help of modern computers, the structure of complexe and quite large networks can now be more easily generated, visualized and analyzed. Even more, as networks are logically equivalent to graphs, knownledge that can be represented as a set of entities with interactions can be represented as a network.

In computational biology, Cytoscape [http://cytoscape.org/] is a very popular open source software platform for network modeling.  for visualizing complex networks and integrating these with any type of attribute data. 

Networks are commonly used to study complex systems in many disciplines such as social science and systems biology [@Bader].

# Loading subnetsim package

As with any R package, the `r packageDescription("subnetsim")[["Package"]]` package should 
first be loaded with the following command:

```{r loadingPackage, warning=FALSE, message=FALSE}
library(subnetsim)
```


# Description of the permutation analysis

The permutation analysis is a statistical significance test in which 
the distribution of the test statistic under the null hypothesis is obtained 
by calculating the values of the test statistic under rearrangement of 
the labels on the observed data points. The rearrangement of the labels is 
done through repeated random sampling [@Legendre1998, pp. 142-157]. 


# Session info

Here is the output of sessionInfo() on the system on which this document 
was compiled:

```{r sessionInfo, echo=FALSE}
sessionInfo()
```


# References

