---
title: "Validating that a specific subnetwork is significantly more connected than randomly selected subnetworks with the same number of nodes"
author:  Pascal Belleau and Astrid Deschênes
output:
  html_document:
    toc: true
bibliography: biblio.bibtex
vignette: >
  %\VignetteIndexEntry{Testing if a subnetwork is significantly more connected than randomly selected subnetworks with the same number of nodes}
  %\VignettePackage{subnetsim}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r style, echo = FALSE, results = 'asis', warning=FALSE, message=FALSE}
library(knitr)
library(subnetsim)
```

<br />

**Package**: `r packageDescription("subnetsim")[["Package"]]` <br />
**Authors**: `r packageDescription("subnetsim")[["Author"]]` <br />
**Version**: `r packageDescription("subnetsim")$Version` <br />
**Compiled date**: `r Sys.Date()` <br />
**License**: `r packageDescription("subnetsim")[["License"]]` <br />


# Licensing 

The *`r packageDescription("subnetsim")[["Package"]]`* package and the underlying 
*`r packageDescription("subnetsim")[["Package"]]`* code 
are distributed under the Artistic license 2.0. You are free to use and 
redistribute this software.


# Introduction

Network science is a cross-disciplinary domain that focuses on the representation, analysis and modeling of complex systems as networks or graphs. Networks are commonly used to study complex systems in many disciplines such as social science, computer science and  life sciences [@Bader].

A network model is a mathematical model that is designed to represent entities and their relationships in a system. A network is a collection of nodes (or vertices or sites or actors) joined by edges (or links or bonds or ties). Throught the help of modern computers, the structure of complexe and quite large networks can now be more easily generated, visualized and analyzed. Even more, as networks are logically equivalent to graphs, knownledge that can be represented as a set of entities with interactions can be represented as a network.

In computational biology, Cytoscape [@Shannon2003] is a very popular open source software platform for network modeling and visualization. Even though Cytoscape was originally designed for biological research, it is a general platform. 

The *`r packageDescription("subnetsim")[["Package"]]`* package uses random sampling to test the hypothesis that a specific 
subnetwork is more connected than randomly selected subnetworks with the same number of nodes. 
Three measures of connectivity are validated: 

* the number of nodes in the subnetwork including all the first-degree neighbor nodes
* the number of links in the subnetwork including all the links of the first-degree neighbor nodes
* the number of links in the subnetwork
    
# SIF Format Input


# Description of the random sampling of subnetworks

The simulated subnetworks are generated by random sampling from a global network. 
The global network must correspond to the network that the tested subnetwork comes from.
Each simulated sunbetwork contains the exact same number of nodes than the real subnetwork. 
The *`r packageDescription("subnetsim")[["Package"]]`* package validates that there is no
two identical simulated subnetworks among all simulated subnetworks.

# Loading subnetsim package

As with any R package, the *`r packageDescription("subnetsim")[["Package"]]`* package should 
first be loaded with the following command:

```{r loadingPackage, warning=FALSE, message=FALSE}
library(subnetsim)
```

# An analysis step by step

## Loading the global network and the tested subnetwork

The networks must be in a SIF format file. The *network()* function 
must be used to load the networks.

```{r loadNetwork, warning=FALSE, message=FALSE, collapse=TRUE, cache=TRUE}
# Access demo files stored in the subnetsim package
networkFile <- system.file("extdata", "demo_network.sif", package="subnetsim")
subnetworkFile <- system.file("extdata", "demo_subnetwork.sif", package="subnetsim")

# Load a global network and its tested subnetwork using 
# SIF format files
demo_network_with_sub <- network(netFileName = networkFile,
                                 subNetFileName = subnetworkFile)

# The returned object is an object of class "network"
class(demo_network_with_sub)
```

## Generating the simulated subnetwork

## Extract information from the simulated subnetwork

## Plot the results

# Session info

Here is the output of sessionInfo() on the system on which this document 
was compiled:

```{r sessionInfo, echo=FALSE}
sessionInfo()
```


# References

